Title

### 2018-08-03 thesis/paper/paper.tex
Corrected require-pattern

For statements the pattern consists of two rules, both utilising the same conjunction \(c = \text{tripleEDB}(S, I, P, V) \wedge C_1 \wedge .. \wedge C_m\) with arbitrary atoms \(C_n\) which is used to test if the triple does not fulfil the requirement. Then rule one
\begin{equation*}
\text{require}(S, t) \leftarrow \text{first}(S) \wedge c
\end{equation*}
states that the statement requires the condition and
\begin{equation*}
\text{require}(O, t) \leftarrow \text{next}(S, O) \wedge \text{require}(S, t) \wedge c
\end{equation*}
propagates this down the statement chain.

For qualifiers the conjunction has to be adapted to \(c_q = \text{qualifierEDB}(S, P, V) \wedge C_1 \wedge .. \wedge C_m \) and the rules are
\begin{equation*}
\text{require}(S, P, V, t) \leftarrow \text{first}(S, P, V) \wedge c
\end{equation*}
\begin{equation*}
\text{require}(O, X, C, t) \leftarrow \text{next}(S, P, V, O, X, C) \wedge \text{require}(S, P, V, t) \wedge c
\end{equation*}

@@

\subsubsection{With separators}\label{subsubsec_with_separators}
To find all violations under separators a number of things have to be considered. Only triples are eligible, since qualifiers cannot have further qualifier, and the order of qualifiers on constrained statements needs to be pre-processed as well since qualifier non-existence is relevant. The pattern needs to be applied for every separator, meaning the conjunction is: \(c_q = \text{qualifierEDB}(S, P, V) \wedge \text{unequal}(P, \text{separatorConstant})\) for each separator in \(S\).\\

@@

\subsection{Mandatory qualifier (Q21510856)}
The mandatory qualifier constraint needs to determine qualifier non-existence on constrained statements to find violations, which is similar to section \ref{subsubsec_with_separators}. All constrained statements and their qualifiers have to be extracted and the order of the qualifiers pre-processed. Inequality must be established between all qualifier properties and the conjunction is \(c_q = \text{qualifierEDB}(S, P, V) \wedge \text{unequal}(P, \text{requiredPropertyConstant})\). With the usual require-pattern for qualifiers and the does\_not\_have rule added for brevity the violations would be
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \text{does\_not\_have}(S, \text{requiredPropertyConstant})
\end{split}
\end{equation*}

>>>>

For statements the pattern consists of two rules, both utilising the same conjunction \(c = C_1 \wedge .. \wedge C_m\) with arbitrary atoms \(C_n\) which is used to test if the statement does not fulfil the requirement. Then rule one
\begin{equation*}
\text{require}(S, t) \leftarrow \text{first}(S, I) \wedge c
\end{equation*}
states that the statement requires the condition and
\begin{equation*}
\text{require}(O, t) \leftarrow \text{next}(S, O) \wedge \text{require}(S, t) \wedge c
\end{equation*}
propagates this down the statement chain.

For qualifiers the rules are
\begin{equation*}
\text{require}(S, P, V, t) \leftarrow \text{first}(S, P, V) \wedge c
\end{equation*}
\begin{equation*}
\text{require}(O, X, C, t) \leftarrow \text{next}(S, P, V, O, X, C) \wedge \text{require}(S, P, V, t) \wedge c
\end{equation*}

@@

\subsubsection{With separators}\label{subsubsec_with_separators}
To find all violations under separators a number of things have to be considered. Only triples are eligible, since qualifiers cannot have further qualifier, and the order of qualifiers on constrained statements needs to be pre-processed as well since qualifier non-existence is relevant. The pattern needs to be applied for every separator, meaning the conjunction is: \(c = \text{qualifierEDB}(S, P, V) \wedge \text{unequal}(P, \text{separatorConstant})\) for each separator in \(S\).\\

@@

\subsection{Mandatory qualifier (Q21510856)}
The mandatory qualifier constraint needs to determine qualifier non-existence on constrained statements to find violations, which is similar to section \ref{subsubsec_with_separators}. All constrained statements and their qualifiers have to be extracted and the order of the qualifiers pre-processed. Inequality must be established between all qualifier properties and the conjunction is \(c = \text{qualifierEDB}(S, P, V) \wedge \text{unequal}(P, \text{requiredPropertyConstant})\). With the usual require-pattern for qualifiers and the does\_not\_have rule added for brevity the violations would be
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \text{does\_not\_have}(S, \text{requiredPropertyConstant})
\end{split}
\end{equation*}
